---
title: "Calculation of RII and ITV in Pairwise Competition within a Homogeneous Environment"
author:
  - Jing Yang
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: no
      smooth_scroll: no
---

\pagebreak 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, eval = F)
# two function
se <- function(x){
  se=sd(x,na.rm=T)/sqrt(length(x[!is.na(x)]))
  return(se)
}

# Function: add star
Wilcox_Star <- function(data) {
  data$star <- ""
  for (i in 1:length(data[, 1])) {
    if (data$p.value[i] < 0.001) {
      data$star[i] <- "***"
    } else if (data$p.value[i] < 0.05) {
      data$star[i] <- "**"
    } else if (data$p.value[i] < 0.01) {
      data$star[i] <- "*"
    } else if (data$p.value[i] < 0.1) {
      data$star[i] <- "."
    }
  }
  return(data)
}
# Function: cube root of data
cube.root <- function(data) {
  cube.data <- (abs(data))^(1/3) * sign(data)
  return(cube.data)
}

```

# Library Packages
```{r, warning=FALSE, message=FALSE, result = 'hide', tidy=TRUE, echo=T}
# library packages
library(ggplot2)
library(patchwork)
library(knitr)
library(kableExtra)
library(hypervolume)
library(snow)
library(parallel)
library(ggsignif)
library(alphahull)
library(RColorBrewer)
library(formatR)
#library(devtools)
#install_github("guochunshen/CV") 
#library(CV)

library(gridExtra)
library(ggpubr)
library(fmsb)
```

# load data
```{r, tidy=TRUE, echo=T, warning=FALSE, message=FALSE}
# Read the data
data <- read.csv("01_raw_data/phaseI_pairwise_homogeneous_raw_data.csv")

# Extract variable names
species <- sort(unique(data$sp))  # Sort and get unique species names
pdname <- sort(unique(data[data$comp_type == "inter", "pdname"]))  # Sort and get unique PD names
trait <- sort(c("SSD", "LTO", "LDMC", "LMA", "LTh", "Chl", "SMC"))  # Sort trait names

# Phylogenetic distance (PD) data
pd.data <- data.frame(
  X = 1:16,
  sp_focal = c("C. myrsinifolia", "C. myrsinifolia", "C. sclerophylla", "H. acerba", 
               "H. acerba", "L. harlandii", "P. sheareri", "P. sheareri", "Q. chenii", 
               "Q. chenii", "Q. chenii", "Q. chenii", "C. glauca", "C. glauca", 
               "C. glauca", "S. superba"),
  sp_target = c("Q. chenii", "C. glauca", "C. glauca", "P. sheareri", "Q. chenii", 
                 "S. superba", "H. acerba", "Q. chenii", "C. myrsinifolia", 
                 "H. acerba", "P. sheareri", "C. glauca", "C. myrsinifolia", 
                 "C. sclerophylla", "Q. chenii", "L. harlandii"),
  PD_name = c("C. myrsinifolia-Q. chenii", "C. myrsinifolia-C. glauca", 
              "C. sclerophylla-C. glauca", "H. acerba-P. sheareri", 
              "H. acerba-Q. chenii", "L. harlandii-S. superba", 
              "P. sheareri-H. acerba", "P. sheareri-Q. chenii", 
              "Q. chenii-C. myrsinifolia", "Q. chenii-H. acerba", 
              "Q. chenii-P. sheareri", "Q. chenii-C. glauca", 
              "C. glauca-C. myrsinifolia", "C. glauca-C. sclerophylla", 
              "C. glauca-Q. chenii", "S. superba-L. harlandii"),
  pair_num = c(1, 2, 3, 4, 5, 6, 4, 7, 1, 5, 7, 8, 2, 3, 8, 6),
  PD = c(177, 89, 177, 585, 354, 471, 585, 585, 177, 354, 585, 177, 89, 177, 177, 471),
  Group = c("GD", "G", "G", "GD", "D", "G", "GD", "GD", "GD", "D", "GD", "GD", "G", "G", "GD", "G")
)

# Species serial numbers and paired species in the treatment group
inter.sp.order <- c(1, 1, 1, 2, 2, 3, 4, 4, 5, 6, 6, 7, 7, 7, 7, 8)
inter.pairsp.order <- c(2, 3, 7, 1, 7, 1, 6, 7, 8, 4, 7, 1, 2, 4, 6, 5)
sppairs <- data.frame(pair_num = 1:8,
                      sp1 = species[c(2, 2, 3, 6, 4, 8, 6, 1)],
                      sp2 = species[c(7, 1, 1, 4, 7, 5, 7, 7)],
                      intra_sp1 = c(2, 2, 3, 6, 4, 8, 6, 1),
                      intra_sp2 = c(7, 1, 1, 4, 7, 5, 7, 7),
                      inter_sp1 = c(5, 4, 6, 10, 8, 16, 11, 3),
                      inter_sp2 = c(13, 1, 2, 7, 14, 9, 15, 12))

pair_code <- c("MC", "MG", "SG", "SA", "CA", "SH", "SC", "GC")  # Pair code

# File name
dir.name <- paste0("02_output_results/Exp1_2sp_homo/")
dir.create(dir.name)  # Create directory
write.table(trait, file = paste0(dir.name, "/trait.name.txt"))  # Write trait names to file

```

# Data analyses  
## Estimating competition intensity  
We calculated Relative Interaction Intensity (RII) by $RII={(BM_{alone}-BM_{pair})\over(BM_{alone}+BM_{pair})}$ (Cristina, 2004) based on individual biomass for each tree and each species and divided the two species planted in pairs into superior and inferior species.
```{r, tidy=TRUE, warning=FALSE, echo=T}
# Calculate relative interspecies intensity (RII) for each seedling
result <- data.frame()

# Loop through each species
for (i in 1:length(species)) {
  spi <- data[data$sp == species[i], ]  # Subset data for the current species
  spi$RII <- 0
  spi$lnRR <- 0
  spi$NIntC <- 0
  spi.alone <- spi[spi$comp_type == "alone", ]  # Subset for seedlings grown alone
  spi.inter <- spi[spi$comp_type == "inter", ]  # Subset for seedlings in interspecies competition

  alone.biomass <- mean(spi.alone$BM, na.rm = TRUE)  # Calculate mean biomass for seedlings grown alone

  # Calculate RII, lnRR, and NIntC for seedlings in interspecies competition
  spi.inter$RII <- (spi.inter$BM - alone.biomass) / (spi.inter$BM + alone.biomass)
  spi.inter$lnRR <- log(alone.biomass / spi.inter$BM)
  spi.inter$NIntC <- 2 * (spi.inter$BM - alone.biomass) / ((spi.inter$BM + alone.biomass) + abs(spi.inter$BM - alone.biomass))

  # Combine results for seedlings grown alone and in interspecies competition
  result <- rbind(result, spi.alone, spi.inter)
}

# Assign the calculated results back to the original data
data <- result

# Subset data for interspecies competition
inter.rdata <- data[data$comp_type == "inter", ]

# Calculate mean RII
inter.mean.rii <- tapply(inter.rdata$RII, list(inter.rdata$pdname), mean, na.rm = TRUE)
inter.mean.se <- tapply(inter.rdata$RII, list(inter.rdata$pdname), sd) / sqrt(tapply(inter.rdata$RII, list(inter.rdata$pdname), length))
inter.sample.size <- tapply(inter.rdata$RII, list(inter.rdata$pdname), length)

# Perform Wilcoxon signed-rank test and extract p-values
rii.test <- tapply(inter.rdata$RII, list(inter.rdata$pdname), wilcox.test)
p.value <- sapply(rii.test, function(x) x$p.value)

# Summary
rii.result <- data.frame(species = species[inter.sp.order],
                         pair_sp = species[inter.pairsp.order],
                         comp_type = rep("inter", 2 * length(species)),
                         mean_rii = as.numeric(inter.mean.rii),
                         mean_se = as.numeric(inter.mean.se),
                         sample_size = as.numeric(inter.sample.size),
                         p.value = p.value)
rii.result <- Wilcox_Star(rii.result)
rii.result$pdname <- paste0(rii.result$species, "-", rii.result$pair_sp)

rii.result$pair_num <- NA
rii.result$sp_rank <- NA

# Add serial number of species pairs
for (i in 1:nrow(rii.result)) {
  rii.result$pair_num[i] <- pd.data[pd.data$PD_name == rii.result$pdname[i], "pair_num"]
}

# Determine competitive inferior and superior species based on mean RII
for (i in 1:8) {
  inferior_rii <- min(rii.result[rii.result$pair_num == i, "mean_rii"], na.rm = TRUE)
  rii.result[rii.result$pair_num == i & rii.result$mean_rii == inferior_rii, "sp_rank"] <- "Inferior"
  rii.result[rii.result$pair_num == i & !rii.result$mean_rii == inferior_rii, "sp_rank"] <- "Superior"
}

# Extract indices of inferior and superior species
inferior.num <- as.numeric(rownames(rii.result[rii.result$sp_rank == "Inferior", ]))
superior.num <- as.numeric(rownames(rii.result[rii.result$sp_rank == "Superior", ]))
inter.rii.result <- rii.result

# Split inferior and superior species pairs
rii.result.order <- rii.result[order(rii.result$pair_num), ]
inferior.rii.result <- rii.result.order[rii.result.order$sp_rank == "Inferior", ]
superior.rii.result <- rii.result.order[rii.result.order$sp_rank == "Superior", ]
inter.sp.rank <- data.frame(type = "Low interspecific competition",
                            pair_num = rep(1:8, each = 1),
                            inferior = inferior.rii.result$species,
                            superior = superior.rii.result$species,
                            inferior_rii = round(inferior.rii.result$mean_rii, 2),
                            superior_rii = round(superior.rii.result$mean_rii, 2),
                            inferior_se = round(inferior.rii.result$mean_se, 2),
                            superior_se = round(superior.rii.result$mean_se, 2),
                            inferior_num = round(inferior.rii.result$sample_size, 2),
                            superior_num = round(superior.rii.result$sample_size, 2),
                            p_value = p.value)
inter.rii <- inter.sp.rank
inter.rii$inferior_rii <- paste0(round(inter.rii$inferior_rii, 3), inter.rii$inferior_star)
inter.rii$superior_rii <- paste0(round(inter.rii$superior_rii, 3), inter.rii$superior_star)
inter.rii <- inter.rii[, 1:10]
inter.rii$inf_sup_diff <- NA

# Test for significant difference in competition intensity between inferior and superior species
for (i in 1:8) {
  sp1 <- paste0(sppairs$sp1[i], "-", sppairs$sp2[i])
  sp2 <- paste0(sppairs$sp2[i], "-", sppairs$sp1[i])
  sp1.rii <- inter.rdata[inter.rdata$pdname == sp1, "RII"]
  sp2.rii <- inter.rdata[inter.rdata$pdname == sp2, "RII"]
  wt <- wilcox.test(sp1.rii, sp2.rii)
  inter.rii$inf_sup_diff[i] <- round(wt$p.value, 3)
}

# Write results to a CSV file
write.csv(inter.rii, file = paste0(dir.name, "/Table1. inter_RII_2sp.csv"))
kableExtra::kable(inter.rii[, -1], caption = "RII of competing species in a two-species competition experiment")
inter.riit <- inter.rii

```

## Trait data transformation
```{r, tidy=TRUE, warning=FALSE, echo=T}
# Scaling and centering raw trait data (Z-scores) for calculating hypervolume
for(i in 1:length(trait)){
  t <- data[,colnames(data)==trait[i]]  # Extract the trait column
  m <- mean(t, na.rm = TRUE)  # Calculate mean
  s <- sd(t, na.rm = TRUE)  # Calculate standard deviation
  t[t > (m + 4 * s) | t < (m - 4 * s)] <- NA  # Replace extreme values with NA
  data[,colnames(data)==trait[i]] <- t  # Assign modified column back to data
}

# Remove an outlier (1.47) in the 'SSD' column for the CM-CG pair, which is greater than three times the standard deviation
out_wd <- max(data[data$pdname == "C. glauca-C. myrsinifolia" & data$comp_type == "inter", ]$SSD, na.rm = TRUE)
data_subset <- subset(data, pdname == "C. glauca-C. myrsinifolia" & comp_type == "inter" & SSD == out_wd)
data_subset$SSD <- NA

# Remove rows with missing values
data <- na.omit(data)

# Scale data for hypervolume calculation
hv.data <- data
hv.data[, colnames(hv.data) %in% trait] <- scale(hv.data[, colnames(hv.data) %in% trait])

# Data under different treatments
alone.hdata <- hv.data[hv.data$comp_type == "alone", ]
alone.hdata$pair_num <- NA
inter.hdata <- hv.data[hv.data$comp_type == "inter", ]

# Scale data for treatments
t.data <- data
for (i in 1:length(trait)) {
    traiti <- data[, colnames(data) == trait[i]]
    t.data[, colnames(t.data) == trait[i]] <- (traiti - min(traiti, na.rm = TRUE)) / (max(traiti, na.rm = TRUE) - min(traiti, na.rm = TRUE))
}
```

## Calculating intraspecific trait variability (ITV)
### Hypervolume based on all seven traits
```{r, tidy=TRUE, warning=FALSE, echo=T}
# Core function only returns hypervolume value and mean RII for each sampling
Hypervolume_value <- function(ni, data, trait, sample_size, quantile) {
  if (length(ni) > 2) {  # Check if the number of individuals is greater than 2
    data <- data[ni, ]  # Subset data for selected individuals
    if (sample_size == "all") {
      sample_data <- data[, colnames(data) %in% trait]  # Use all individuals
    } else {
      ind_num <- length(data[, 1])  # Total number of individuals
      sample_num <- sample(1:ind_num, sample_size)  # Randomly select sample_size individuals
      sample_data <- data[sample_num, colnames(data) %in% trait]  # Subset data for selected individuals
      sample_rii <- mean(data[sample_num, ]$RII, na.rm = TRUE)  # Calculate mean RII for selected individuals
    }
    bandwidth <- estimate_bandwidth(data = sample_data)  # Estimate bandwidth for hypervolume calculation
    hypervolume <- hypervolume_gaussian(data = sample_data, name = unique(sample_data$pdname),
                                        kde.bandwidth = bandwidth, quantile.requested = quantile)  # Calculate hypervolume
    hv <- hypervolume@Volume  # Extract hypervolume value
  } else {
    hv <- NA  # If the number of individuals is less than or equal to 2, assign NA to hypervolume
    sample_rii <- NA  # Assign NA to mean RII
  }
  return(c(hv = hv, rii = sample_rii))  # Return a vector containing hypervolume value and mean RII
}

# Function to simulate hypervolume
Sim_Hypervolume <- function(n, data, trait, sample_size, quantile, Hypervolume_value) {
  library(hypervolume)
  # Apply Hypervolume_value function to each replicate and return hypervolume and RII values
  hvs <- tapply(1:nrow(data), list(data$pdname), Hypervolume_value, data, trait, sample_size, quantile)
  return(hvs)
}

# Set parameters
quantile <- 0.95  # Quantile value for hypervolume calculation
sample_size <- 20  # Sample size
Nrep <- 999  # Number of replications
clnum <- detectCores() - 1  # Number of CPU cores to be used
cl <- makeCluster(getOption("cl.cores", 60))  # Initialize cluster

# Load saved data if exists
if (file.exists(file = paste0(dir.name, "/HV_RII.RData"))) {
  load(paste0(dir.name, "/HV_RII.RData"))  # Load previously saved data
} else {
  # Perform simulations and save data
  set.seed(rnorm(1))  # Set random seed
  Sys.time()  # Current system time
  # Calculate hypervolume and RII for alone and interspecies conditions using parallel processing
  alone.hv <- parLapply(cl, 1:Nrep, Sim_Hypervolume, alone.hdata, trait, sample_size, quantile, Hypervolume_value)
  inter.hv <- parLapply(cl, 1:Nrep, Sim_Hypervolume, inter.hdata, trait, sample_size, quantile, Hypervolume_value)
  # Save calculated data
  save(trait, alone.hv, inter.hv, file = paste0(dir.name, "/HV_RII.RData"))
}

# Organize hypervolume and RII data
alone.hvrii <- matrix(unlist(alone.hv), nrow = length(species) * 2, dimnames = list(rep(species, each = 2), 1:Nrep))
inter.hvrii <- matrix(unlist(inter.hv), nrow = length(species) * 2 * 2, dimnames = list(rep(pdname, each = 2), 1:Nrep))

# Extract hypervolume and RII separately for alone treatments
alone.hv <- alone.hvrii[seq(1, 16, 2), ]
alone.rii <- alone.hvrii[seq(2, 16, 2), ]
# Repeat the hypervolume and RII data for each pairwise comparison in inter treatments
alone.hv <- matrix(rep(unlist(alone.hv), rep(table(inter.sp.order), Nrep)), nrow = length(pdname), 
                   dimnames = list(species[inter.sp.order], 1:Nrep))
alone.rii <- matrix(rep(unlist(alone.rii), rep(table(inter.sp.order), Nrep)), nrow = length(pdname), 
                    dimnames = list(species[inter.sp.order], 1:Nrep))

# Extract hypervolume and RII separately for inter treatments
inter.hv <- inter.hvrii[seq(1, 32, 2), ]
inter.rii <- inter.hvrii[seq(2, 32, 2), ]

# Organize data for HV and ContrHV
hv.box.data <- data.frame(
  Nrep = rep(1:Nrep, each = 16),  # Replicate number
  pdname = rep(pdname, Nrep),  # Pairwise comparison name
  sp = rep(species[inter.sp.order], Nrep),  # Species name
  sp_group = rep(inter.rii.result$sp_rank, Nrep),  # Species group based on RII
  pair_code = rep(c("MG", "SG", "GC", "MG", "MC", "SG", "SA", "CA", "SH", "SA", "SC", "GC", "MC", "CA", "SC", "SH"), Nrep),  # Pair code
  alone_hv = as.numeric(alone.hv),  # Hypervolume for alone treatment
  inter_hv = as.numeric(inter.hv),  # Hypervolume for interspecies treatment
  alone_rii = as.numeric(alone.rii),  # RII for alone treatment
  inter_rii = as.numeric(inter.rii)  # RII for interspecies treatment
)

# Convert 'pair_code' to factor with specified levels
hv.box.data$pair_code <- factor(hv.box.data$pair_code, levels = pair_code)
# Convert 'sp_group' to character
hv.box.data$sp_group <- as.character(hv.box.data$sp_group)

# HV change
## Calculate the change in MTS based on the mean of 9 random trials
mean.alone.hv <- apply(alone.hv, 1, mean)  # Calculate mean hypervolume for alone treatment
inter.hvchange <- (as.numeric(inter.hv) - rep(mean.alone.hv, Nrep))  # Calculate hypervolume change for interspecies treatment
# Create a data frame for hypervolume change
hvchange.box.data <- data.frame(
  pdname = rep(pdname, Nrep),  # Pairwise comparison name
  sp = rep(species[inter.sp.order], Nrep),  # Species name
  sp_group = rep(rii.result$sp_rank, Nrep),  # Species group based on RII
  pair_code = rep(c("MG", "SG", "GC", "MG", "MC", "SG", "SA", "CA", "SH", "SA", "SC", "GC", "MC", "CA", "SC", "SH"), Nrep),  # Pair code
  inter_hvchange = inter.hvchange,  # Hypervolume change for interspecies treatment
  inter_mean_rii = as.numeric(inter.rii),  # Mean RII for interspecies treatment
  rii = rep(rii.result$mean_rii, Nrep)  # Mean RII for all pairwise comparisons
)
# Convert 'pair_code' to factor with specified levels
hvchange.box.data$pair_code <- factor(hvchange.box.data$pair_code, levels = pair_code)
hvchange.box.data$sp_group <- as.character(hvchange.box.data$sp_group)  # Convert 'sp_group' to character

## Convert pair_code information to numbers for ease of adding significance comparison results
new_pair_code <- 1:8  # New numeric levels for pair code
# Convert 'pair_code' to numeric with specified levels
hv.box.data1 <- hv.box.data
hv.box.data <- data.frame()
for (i in 1:8) {
  pairi <- hv.box.data1[hv.box.data1$pair_code == pair_code[i], ]
  pairi$pair_code <- new_pair_code[i]
  hv.box.data <- rbind(hv.box.data, pairi)
}
hv.box.data$pair_code <- factor(hv.box.data$pair_code, levels = new_pair_code)  # Convert 'pair_code' to factor with numeric levels

# Convert pair code information to numbers for ease of adding significance comparison results
new_pair_code <- 1:8  # New numeric levels for pair code
hvchange.box.data1 <- hvchange.box.data
hvchange.box.data <- data.frame()
for (i in 1:8) {
  pairi <- hvchange.box.data1[hvchange.box.data1$pair_code == pair_code[i], ]
  pairi$pair_code <- new_pair_code[i]
  hvchange.box.data <- rbind(hvchange.box.data, pairi)
}
hv.box.data$pair_code <- factor(hv.box.data$pair_code, levels = new_pair_code)  # Convert 'pair_code' to factor with numeric levels
```

### Hypervolume Visualisation based on PC1-PC3
```{r, tidy=TRUE, warning=FALSE, echo=T}
# Principal component analysis
# Extract trait data from hv.data based on provided traits
trait.data <- hv.data[, colnames(hv.data) %in% trait, ]
# Perform principal component analysis (PCA) on the trait data with correlation matrix
trait.stand.pr <- princomp(trait.data, cor = TRUE)
# Summarize PCA results including loadings
pr <- summary(trait.stand.pr, loadings = TRUE)

# Store PC scores in the dataset
hv.data$PC1 <- pr$scores[, 1]
hv.data$PC2 <- pr$scores[, 2]
hv.data$PC3 <- pr$scores[, 3]
trait1 <- c("PC1", "PC2", "PC3")  # Names of PC traits

# If PCA results are used, visualize them with a plot for better interpretation
alone.hdata <- hv.data[hv.data$comp_type == "alone", ]  # Subset for alone condition
inter.hdata <- hv.data[hv.data$comp_type == "inter", ]  # Subset for interspecies condition

# Function to calculate hypervolume for all individuals to create a scatter plot (gaussian)
Hyperv <- function(ni, data, trait, quantile) {
  data <- data[ni, ]
  sample_data <- data[, colnames(data) %in% trait]
  bandwidth <- estimate_bandwidth(data = sample_data)
  hv <- hypervolume_gaussian(data = sample_data, name = unique(sample_data$sp),
                             kde.bandwidth = bandwidth, quantile.requested = quantile)
  return(hv)
}
trait1 <- c("PC1", "PC2", "PC3")  # Names of PC traits

# Check if the hypervolume data has already been saved, otherwise calculate and save it
if (file.exists(file = paste0(dir.name, "/hv_pointsplot_pc13.RData"))) {
  load(paste0(dir.name, "/hv_pointsplot_pc13.RData"))  # Load previously saved data
} else {
  alone.hvp <- tapply(1:nrow(alone.hdata), list(alone.hdata$sp), Hyperv, alone.hdata, trait1, 0.95)
  inter.hvp <- tapply(1:nrow(inter.hdata), list(inter.hdata$pdname), Hyperv, inter.hdata, trait1, 0.95)
  save(alone.hvp, inter.hvp, file = paste0(dir.name, "/hv_pointsplot_pc13.RData"))  # Save calculated data
}

```

### ITV based on individual trait
```{r, tidy=TRUE, warning=FALSE, echo=T}
#### CV4 based on a single trait
# Core function to calculate CV4(Bao's CV)
CV4 <- function(trait_sample) {
  trait_sample <- trait_sample[!is.na(trait_sample)]  # Remove NA values
  if (length(trait_sample) > 1) {  # Ensure there are more than 1 data point
    N <- length(trait_sample)
    # calculate CV^2
    y_bar <- mean(trait_sample)  # Mean of trait values
    s2_hat <- var(trait_sample)  # Sample variance
    cv_2 <- s2_hat / y_bar^2  # Coefficient of variation squared
    cv_1 <- sqrt(cv_2)  # Coefficient of variation
    gamma_1 <- sum(((trait_sample - y_bar) / s2_hat^0.5)^3) / N  # Skewness
    gamma_2 <- sum(((trait_sample - y_bar) / s2_hat^0.5)^4) / N  # Kurtosis
    bias2 <- cv_1^3 / N - cv_1 / 4 / N - cv_1^2 * gamma_1 / 2 / N - cv_1 * gamma_2 / 8 / N  # Bias correction
    cv4 <- cv_1 - bias2  # Corrected coefficient of variation
  } else {
    cv4 <- NA  # If there's only one data point, return NA
  }
  return(cv4)
}

# Function to calculate mean of ITV for a given sample size(N) based on trait data
Sample_CV <- function(data, N) {
  if (N == "all") {
    cv4.mean <- CV4(data)  # Calculate CV4 for entire dataset
  } else {
    cv <- replicate(5, CV4(sample(data, N)))  # Calculate CV4 for multiple samples and replicate 5 times
    cv4.mean <- mean(cv)  # Calculate mean of replicated CV4 values
  }
  return(cv4.mean)
}

nrep <- 999  # Number of replications
sample_size <- 15  # Sample size
t.data$sp <- factor(t.data$sp, levels = species)  # Convert species column to factor with specified levels
t.data$comp_type <- factor(t.data$comp_type, levels = c("alone", "inter"))  # Convert comp_type column to factor with specified levels

# Check if CV4 results are already saved, otherwise calculate them
if (file.exists(file = paste0(dir.name, "/CV4.RData"))) {
  load(paste0(dir.name, "/CV4.RData"))  # Load previously saved CV4 results
} else {
  alone.cv <- matrix(NA, ncol = 7, nrow = 8, dimnames = list(species, trait))  # Initialize matrix to store CV4 results for alone condition
  alone.cdata <- t.data[t.data$comp_type == "alone", ]  # Subset data for alone condition
  for (t in 1:length(trait)) {
    c <- replicate(nrep, tapply(alone.cdata[, trait[t]], list(alone.cdata$sp), Sample_CV, sample_size))  # Calculate CV4 for each species
    alone.cv[, t] <- apply(c, 1, mean, na.rm = TRUE)  # Calculate mean CV4 across replications for each species
  }

  inter.cv <- matrix(NA, ncol = 7, nrow = 16, dimnames = list(pdname, trait))  # Initialize matrix to store CV4 results for interspecies condition
  inter.cdata <- t.data[t.data$comp_type == "inter", ]  # Subset data for interspecies condition
  for (t in 1:length(trait)) {
    c <- replicate(nrep, tapply(inter.cdata[, trait[t]], list(inter.cdata$pdname), Sample_CV, sample_size))  # Calculate CV4 for each species pair
    inter.cv[, t] <- apply(c, 1, mean, na.rm = TRUE)  # Calculate mean CV4 across replications for each species pair
  }

  save(alone.cv, inter.cv, file = paste0(dir.name, "/CV4.RData"))  # Save calculated CV4 results
}

alone.cv1 <- as.data.frame(alone.cv[inter.sp.order, ])  # Reorder alone CV4 results based on interspecies order
alone.cv1$sp_group <- inter.rii.result$sp_rank  # Add species group information based on interspecies competition
inter.cv1 <- as.data.frame(inter.cv)  # Convert interspecies CV4 results to data frame
inter.cv1$sp_group <- inter.rii.result$sp_rank  # Add species group information based on interspecies competition

inf_alone_varimp <- alone.cv1[alone.cv1$sp_group == "Inferior", ][, -8]  # Subset CV4 results for inferior species in alone condition
sup_alone_varimp <- alone.cv1[alone.cv1$sp_group == "Superior", ][, -8]  # Subset CV4 results for superior species in alone condition
inf_inter_varimp <- inter.cv1[inter.cv1$sp_group == "Inferior", ][, -8]  # Subset CV4 results for inferior species in interspecies condition
sup_inter_varimp <- inter.cv1[inter.cv1$sp_group == "Superior", ][, -8]  # Subset CV4 results for superior species in interspecies condition

alone.varimp <- alone.cv1[, -8]  # Exclude species group column from alone CV4 results
inter.varimp <- inter.cv1[, -8]  # Exclude species group column from interspecies CV4 results
colnames(alone.varimp)[6:7] <- c("SSD", "SMC")  # Rename columns for ease of interpretation
colnames(inter.varimp)[6:7] <- c("SSD", "SMC")  # Rename columns for ease of interpretation

colnames(inf_alone_varimp)[6:7] <- c("SSD", "SMC")  # Rename columns for ease of interpretation
colnames(sup_alone_varimp)[6:7] <- c("SSD", "SMC")  # Rename columns for ease of interpretation
colnames(inf_inter_varimp)[6:7] <- c("SSD", "SMC")  # Rename columns for ease of interpretation
colnames(sup_inter_varimp)[6:7] <- c("SSD", "SMC")  # Rename columns for ease of interpretation

##### Calculate mean varimp
inf_alone_varimp[9, ] <- apply(inf_alone_varimp, 2, mean)  # Calculate mean CV4 for inferior species in alone condition
sup_alone_varimp[9, ] <- apply(sup_alone_varimp, 2, mean)  # Calculate mean CV4 for superior species in alone condition
inf_inter_varimp[9, ] <- apply(inf_inter_varimp, 2, mean)  # Calculate mean CV4 for inferior species in interspecies condition
sup_inter_varimp[9, ] <- apply(sup_inter_varimp, 2, mean)  # Calculate mean CV4 for superior species in interspecies condition
```

# save results for 7-dimensional hypervolume (ITV) and RII
```{r, tidy=T, echo=T}
# Save the following objects to a .RData file for future use
save(species, pdname, pd.data, trait, sppairs, rii.result, inter.riit,
  hv.box.data, hvchange.box.data, alone.hvp, inter.hvp,
  alone.varimp, inter.varimp, inf_alone_varimp, sup_alone_varimp,
  inf_inter_varimp, sup_inter_varimp, se, cube.root, Wilcox_Star,
  scale_fill_Publication, scale_colour_Publication,
  f.dir.name, dir.name,
  file = "02_output_results/output_allresults_2sp_homo.RData"
)

trait.2sp <- trait
species.2sp <- species

hv.box.data.2sp <- hv.box.data
hvchange.box.data.2sp <- hv.box.data

alone.hvp.2sp <- alone.hvp
inter.hvp.2sp <- inter.hvp

alone.varimp.2sp <- alone.varimp
inter.varimp.2sp <- inter.varimp

scale_fill_Publication.2sp <- scale_fill_Publication
scale_colour_Publication.2sp <- scale_colour_Publication
dir.name.2sp <- dir.name
```

# Calculating hypervolume based on reduced-dimensional hypervolume (PC1, PC2, PC3)
```{r, tidy=TRUE, warning=FALSE, echo=T}
trait1 <- c("PC1", "PC2", "PC3") # reduced traits

# Set parameters
quantile <- 0.95  # Quantile value for hypervolume calculation
sample_size <- 20  # Sample size
Nrep <- 999  # Number of replications
clnum <- detectCores() - 1  # Number of CPU cores to be used
cl <- makeCluster(getOption("cl.cores", 60))  # Initialize cluster

# Load saved data if exists
if (file.exists(file = paste0(dir.name, "/HV_RII_PCA3.RData"))) {
  load(paste0(dir.name, "/HV_RII_PCA3.RData"))  # Load previously saved data
} else {
  # Perform simulations and save data
  set.seed(rnorm(1))  # Set random seed
  Sys.time()  # Current system time
  # Calculate hypervolume and RII for alone and interspecies conditions using parallel processing
  alone.hv <- parLapply(cl, 1:Nrep, Sim_Hypervolume, alone.hdata, trait1, sample_size, quantile, Hypervolume_value)
  inter.hv <- parLapply(cl, 1:Nrep, Sim_Hypervolume, inter.hdata, trait1, sample_size, quantile, Hypervolume_value)
  # Save calculated data
  save(trait, alone.hv, inter.hv, file = paste0(dir.name, "/HV_RII_PCA3.RData"))
}

# Organize hypervolume and RII data
alone.hvrii <- matrix(unlist(alone.hv), nrow = length(species) * 2, dimnames = list(rep(species, each = 2), 1:Nrep))
inter.hvrii <- matrix(unlist(inter.hv), nrow = length(species) * 2 * 2, dimnames = list(rep(pdname, each = 2), 1:Nrep))

# Extract hypervolume and RII separately for alone treatments
alone.hv <- alone.hvrii[seq(1, 16, 2), ]
alone.rii <- alone.hvrii[seq(2, 16, 2), ]
# Repeat the hypervolume and RII data for each pairwise comparison in inter treatments
alone.hv <- matrix(rep(unlist(alone.hv), rep(table(inter.sp.order), Nrep)), nrow = length(pdname), 
                   dimnames = list(species[inter.sp.order], 1:Nrep))
alone.rii <- matrix(rep(unlist(alone.rii), rep(table(inter.sp.order), Nrep)), nrow = length(pdname), 
                    dimnames = list(species[inter.sp.order], 1:Nrep))

# Extract hypervolume and RII separately for inter treatments
inter.hv <- inter.hvrii[seq(1, 32, 2), ]
inter.rii <- inter.hvrii[seq(2, 32, 2), ]

# Organize data for HV and ContrHV
hv.box.data <- data.frame(
  Nrep = rep(1:Nrep, each = 16),  # Replicate number
  pdname = rep(pdname, Nrep),  # Pairwise comparison name
  sp = rep(species[inter.sp.order], Nrep),  # Species name
  sp_group = rep(inter.rii.result$sp_rank, Nrep),  # Species group based on RII
  pair_code = rep(c("MG", "SG", "GC", "MG", "MC", "SG", "SA", "CA", "SH", "SA", "SC", "GC", "MC", "CA", "SC", "SH"), Nrep),  # Pair code
  alone_hv = as.numeric(alone.hv),  # Hypervolume for alone treatment
  inter_hv = as.numeric(inter.hv),  # Hypervolume for interspecies treatment
  alone_rii = as.numeric(alone.rii),  # RII for alone treatment
  inter_rii = as.numeric(inter.rii)  # RII for interspecies treatment
)

# Convert 'pair_code' to factor with specified levels
hv.box.data$pair_code <- factor(hv.box.data$pair_code, levels = pair_code)
# Convert 'sp_group' to character
hv.box.data$sp_group <- as.character(hv.box.data$sp_group)

# HV change
## Calculate the change in MTS based on the mean of 9 random trials
mean.alone.hv <- apply(alone.hv, 1, mean)  # Calculate mean hypervolume for alone treatment
inter.hvchange <- (as.numeric(inter.hv) - rep(mean.alone.hv, Nrep))  # Calculate hypervolume change for interspecies treatment
# Create a data frame for hypervolume change
hvchange.box.data <- data.frame(
  pdname = rep(pdname, Nrep),  # Pairwise comparison name
  sp = rep(species[inter.sp.order], Nrep),  # Species name
  sp_group = rep(rii.result$sp_rank, Nrep),  # Species group based on RII
  pair_code = rep(c("MG", "SG", "GC", "MG", "MC", "SG", "SA", "CA", "SH", "SA", "SC", "GC", "MC", "CA", "SC", "SH"), Nrep),  # Pair code
  inter_hvchange = inter.hvchange,  # Hypervolume change for interspecies treatment
  inter_mean_rii = as.numeric(inter.rii),  # Mean RII for interspecies treatment
  rii = rep(rii.result$mean_rii, Nrep)  # Mean RII for all pairwise comparisons
)
# Convert 'pair_code' to factor with specified levels
hvchange.box.data$pair_code <- factor(hvchange.box.data$pair_code, levels = pair_code)
hvchange.box.data$sp_group <- as.character(hvchange.box.data$sp_group)  # Convert 'sp_group' to character

## Convert pair_code information to numbers for ease of adding significance comparison results
new_pair_code <- 1:8  # New numeric levels for pair code
# Convert 'pair_code' to numeric with specified levels
hv.box.data1 <- hv.box.data
hv.box.data <- data.frame()
for (i in 1:8) {
  pairi <- hv.box.data1[hv.box.data1$pair_code == pair_code[i], ]
  pairi$pair_code <- new_pair_code[i]
  hv.box.data <- rbind(hv.box.data, pairi)
}
hv.box.data$pair_code <- factor(hv.box.data$pair_code, levels = new_pair_code)  # Convert 'pair_code' to factor with numeric levels

# Convert pair code information to numbers for ease of adding significance comparison results
new_pair_code <- 1:8  # New numeric levels for pair code
hvchange.box.data1 <- hvchange.box.data
hvchange.box.data <- data.frame()
for (i in 1:8) {
  pairi <- hvchange.box.data1[hvchange.box.data1$pair_code == pair_code[i], ]
  pairi$pair_code <- new_pair_code[i]
  hvchange.box.data <- rbind(hvchange.box.data, pairi)
}
hv.box.data$pair_code <- factor(hv.box.data$pair_code, levels = new_pair_code)  # Convert 'pair_code' to factor with numeric levels
```

# save results for reduced-dimensional hypervolume (ITV) and RII
```{r, tidy=T, echo=T}
# Save the following objects to a .RData file for future use
save(species, pdname, pd.data, trait, sppairs, rii.result, inter.riit,
  hv.box.data, hvchange.box.data, alone.hvp, inter.hvp,
  alone.varimp, inter.varimp, inf_alone_varimp, sup_alone_varimp,
  inf_inter_varimp, sup_inter_varimp, se, cube.root, Wilcox_Star,
  scale_fill_Publication, scale_colour_Publication,
  f.dir.name, dir.name,
  file = "02_output_results/output_allresults_2sp_homo_PCA3.RData"
)
```

